HBCC - DLPFC - FEATURECOUNTS - GRCh38 - CQN

### 2020-05-16 individual-cohorts/HBCC_DLPFC_FEATURECOUNTS_GRCh38_CQN.Rmd
fails with random effects

#### Phase II (batch effects)
```{r phase2}
# Fit a base model with the following covariates
phase2 <- mvIC::mvForwardStepwise(exprObj = CQN.GENE_EXPRESSION$E,
                         baseFormula = phase1$formula, 
                         data = COVARIATES,
                         variables = array(c("(1|LibraryBatch)", "(1|FlowcellBatch)")))
kable(phase2$settings)
kable(phase2$trace)
as.character(phase2$formula)[2]
```

>>>>

#### Phase II (batch effects)
```{r phase2}
# Fit a base model with the following covariates
phase2 <- mvIC::mvForwardStepwise(exprObj = CQN.GENE_EXPRESSION$E,
                         baseFormula = phase1$formula, 
                         data = COVARIATES,
                         variables = array(c("LibraryBatch", "FlowcellBatch")))
kable(phase2$settings)
kable(phase2$trace)
as.character(phase2$formula)[2]
```
